[dcpo_demsupport]

### 2020-09-30 paper/dcpo_demsupport.Rmd
finish the appendix tables

df_tableAJPS <- df_plotS %>% mutate(
  std.error = ifelse(is.na(std.error), se, std.error)
) %>% 
  select(term, estimate, std.error, model)

@@

@@

@@

@@

```{r tableAJPS}

@@

>>>>

df_tableAJPS <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "Pooled"
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up")

@@

df_tableAJPS <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "Regime Spec."
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up") %>% 
  bind_rows(df_tableAJPS) %>% 
  mutate(estimate = round(estimate, digits = 3))

@@

df_tableAPSR <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "Basic"
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up")

@@

df_tableAPSR <- df_plotS %>% mutate(
  conf = paste0("[", round(conf.low, digits = 2), ", ", round(conf.high, digits = 2), "]"),
  group = "W. Corruption"
) %>% 
  select(term, estimate, conf, n, model, group) %>% 
  fill(n, .direction = "up") %>% 
  bind_rows(df_tableAPSR) %>% 
  mutate(estimate = round(estimate, digits = 3))

@@

```{r tableAJPS}
df_tableAJPS %>% 
  mutate(estimate = paste0(estimate, "\n ", conf),
         group = paste0(group, "\n (n: ", n, ")")) %>% 
  arrange(group, model) %>% 
  select(group, model, term, estimate) %>% 
  group_by(group) %>% 
  pivot_wider(names_from = model, values_from = estimate) %>% 
  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
  arrange(group) %>% 
  flextable %>% 
  set_header_labels(group = "Model",
                    term = "Variable") %>% 
  merge_v(j = c("group")) %>% 
  hline(i = 8, border = officer::fp_border()) %>% 
  autofit() %>% 
  add_header_lines(values = paste0("Number of Observations: ", unique(df_tableAJPS$n)))
```

@@

```{r table APSR}
df_tableAPSR %>% 
  mutate(estimate = paste0(estimate, "\n ", conf),
         group = paste0(group, "\n (n: ", n, ")")) %>% 
  arrange(group, model) %>% 
  select(group, model, term, estimate) %>% 
  group_by(group) %>% 
  pivot_wider(names_from = model, values_from = estimate) %>% 
  mutate(term = str_replace_all(term, "\\n", " ")) %>% 
  arrange(group) %>% 
  flextable %>% 
  set_header_labels(group = "Model",
                    term = "Variable") %>% 
  merge_v(j = c("group")) %>% 
  hline(i = 8, border = officer::fp_border()) %>% 
  autofit() 
```
